Global Value Chain Analysis of LMICs

### 2015-04-22 OECD-TiVa-LMIC-GVCs.Rmd
add website and thank you
remove notices

 ```{r}
 library(decompr)
 ls.str("package:decompr")
 ```

@@

 ```{r}
 library(gvc)
 ls.str("package:gvc")
 ```

@@

```{r, echo=FALSE}
w1995_2008 %>%
  group_by(year) %>%
  summarise( PDC = ( sum(DDC_FIN) + sum(DDC_INT) + sum(ODC) + sum(MDC) ) / sum(texp) ) %>%
  ggvis(~year, ~PDC) %>%
  layer_lines()
```

@@

```{r, echo=FALSE}
# i2e by industry
gvc_indicators %>%
  group_by(ind_name) %>%
  summarise(i2e = sum(fvax_ams_ik) * 100 / sum(exports_ik) ) %>%
  top_n(10) %>%
  ggvis(~factor(ind_name), ~i2e) %>%
  layer_bars() %>%
  add_axis("x", title = "industry name")
```

@@

```{r, echo=FALSE}
# e2r by industry
gvc_indicators %>%
  group_by(ind_name) %>%
  filter(ind_name != "pvh" & ind_name != "edu" & ind_name != "egw" & ind_name != "con" & ind_name != "rea" & ind_name != "gov" & ind_name != "hth" & ind_name != "ptl") %>%
  summarise(e2r = sum(dvar_ik) * 100 / sum(exports_ik) ) %>%
  top_n(10) %>%
  ggvis(~factor(ind_name), ~e2r) %>%
  layer_bars() %>%
  add_axis("x", title = "industry name")
```

@@

```{r, echo=FALSE}
gvc_indicators %>%
  group_by(ctry) %>%
  summarise(e2r = sum(dvar_ik) / sum(exports_ik), nat_res_exports = mean(nat_res_exp_sha_t_3) ) %>%
  ggvis(~nat_res_exports, ~e2r ) %>%
  layer_points() %>%
  layer_model_predictions(model = "lm")
```

@@

>>>>

 ```{r, tidy=FALSE}
 library(decompr)
 ls.str("package:decompr")
 ```

@@

 ```{r, tidy=FALSE}
 library(gvc)
 ls.str("package:gvc")
 ```

@@

```{r echo=FALSE}
w1995_2008 %>%
  group_by(year) %>%
  summarise( PDC = ( sum(DDC_FIN) + sum(DDC_INT) + sum(ODC) + sum(MDC) ) / sum(texp) ) %>%
  ggvis(~year, ~PDC) %>%
  layer_lines()
```

@@

```{r echo=FALSE, warning=FALSE, message=FALSE}
# i2e by industry
gvc_indicators %>%
  group_by(ind_name) %>%
  summarise(i2e = sum(fvax_ams_ik) * 100 / sum(exports_ik) ) %>%
  top_n(10) %>%
  ggvis(~factor(ind_name), ~i2e) %>%
  layer_bars() %>%
  add_axis("x", title = "industry name")
```

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# e2r by industry
gvc_indicators %>%
  group_by(ind_name) %>%
  filter(ind_name != "pvh" & ind_name != "edu" & ind_name != "egw" & ind_name != "con" & ind_name != "rea" & ind_name != "gov" & ind_name != "hth" & ind_name != "ptl") %>%
  summarise(e2r = sum(dvar_ik) * 100 / sum(exports_ik) ) %>%
  top_n(10) %>%
  ggvis(~factor(ind_name), ~e2r) %>%
  layer_bars() %>%
  add_axis("x", title = "industry name")
```

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
gvc_indicators %>%
  group_by(ctry) %>%
  summarise(e2r = sum(dvar_ik) / sum(exports_ik), nat_res_exports = mean(nat_res_exp_sha_t_3) ) %>%
  ggvis(~nat_res_exports, ~e2r ) %>%
  layer_points() %>%
  layer_model_predictions(model = "lm")
```

@@

  - http://qua.st/decompr

# Thank You!
